A meta-analysis of mental rotation ability in the first years of life

### 2022-04-29 code/analysis.Rmd
Correct heterogeneity and ICC estimates

# Compute intra-class correlation
sd_article <- VarCorr(res_brm)$article$sd
sd_experiment <- VarCorr(res_brm)$`article:experiment`$sd
(icc <- sd_article / (sd_article + sd_experiment))

# Compute probabilities of the meta-analytic being greater than 0
hypothesis(res_brm, "Intercept > 0")$hypothesis
```

@@

# Compute intra-class correlation
sd_article_reg <- VarCorr(res_brm_reg)$article$sd
sd_experiment_reg <- VarCorr(res_brm_reg)$`article:experiment`$sd
(icc_reg <- sd_article_reg / (sd_article_reg + sd_experiment_reg))

# Compute reduction in heterogeneity compared to the original meta-analysis
1 - (sd_article_reg + sd_experiment_reg) / (sd_article + sd_experiment)
```

>>>>

# Compute probabilities of the meta-analytic being greater than 0
hypothesis(res_brm, "Intercept > 0")$hypothesis

# Compute by-experiment variance
var_experiment <- as.matrix(
  res_brm,
  variable = "sd_article:experiment__Intercept"
)^2
mean_qi(var_experiment)

# Compute by-article variance
var_article <- as.matrix(
  res_brm,
  variable = "sd_article__Intercept"
)^2
mean_qi(var_article_draws)

# Compute intra-class correlation
var_total <- (var_experiment + var_article)
icc_draws <- var_article / var_total
mean_qi(icc_draws)
```

@@

# Compute by-experiment variance
var_experiment_reg <- as.matrix(
  res_brm_reg,
  variable = "sd_article:experiment__Intercept"
)^2
mean_qi(var_experiment_reg)

# Compute by-article variance
var_article_reg <- as.matrix(
  res_brm_reg,
  variable = "sd_article__Intercept"
)^2
mean_qi(var_article_reg)

# Compute intra-class correlation
var_total_reg <- var_experiment_reg + var_article_reg
icc_reg <- var_article_reg / var_total_reg
mean_qi(icc_reg)

# Compute reduction in heterogeneity compared to the original meta-analysis
1 - mean(var_total_reg / var_total)
```
